%-------------------------
% Resume in LaTeX — Dheer Guda
% Based on Jake Gutierrez's template (MIT), ATS-friendly
% Compile with: pdflatex resume.tex
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% pdfTeX-only ATS/unicode mapping — skipped under XeTeX/LuaTeX (tectonic),
% which produce unicode-aware PDFs natively.
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Dheer Guda} \\ \vspace{1pt}
    \small
    \href{mailto:gudadheer@gmail.com}{gudadheer@gmail.com} $|$
    (732)-268-0687 $|$
    \href{https://linkedin.com/in/dheer-guda/}{linkedin.com/in/dheer-guda} $|$
    \href{https://dheerguda.com}{dheerguda.com}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland College Park}{College Park, Maryland}
      {B.S. in Computer Science \& Math, Minor in Business Analytics \& Data Science}{Expected Graduation, May 2027}
      \resumeItemListStart
        \resumeItem{\textbf{Honors:} Dean's List, QUEST Honors Program, Startup Shell Grant Winner}
        \resumeItem{\textbf{Related Coursework:} Data Structures \& Algorithms, Operating Systems, Database Design, Machine Learning, Artificial Intelligence, Software Engineering, Probability \& Statistics}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer Intern, Amazon}{Seattle, Washington}
      {LLM Deployment Cost Optimization (MARS)}{}
      \resumeItemListStart
        \resumeItem{Extended MARS, Amazon's internal system for finding a model's cheapest deployment configuration, beyond weight-only optimizations (e.g.\ quantization) by adding knowledge distillation, its first parameter-modifying technique.}
        \resumeItem{Built hard-label, soft-label, and feature-based distillation pipelines with NVIDIA Model-Opt, Axolotl, and LLaMA-Factory to fine-tune the production Qwen 3.5 model that fills missing product type attributes (PTA) on Amazon's catalog.}
        \resumeItem{Designed a pipeline-composition framework spanning Model-Opt techniques (speculative decoding, pruning, quantization, distillation), using heuristic and surrogate-model search to find the best-serving combination.}
      \resumeItemListEnd

    \resumeSubheading
      {CEO, Synari}{College Park, Maryland}
      {AI-Powered Practice Management Startup for Cognitive Therapy (\href{https://synari.org}{synari.org})}{}
      \resumeItemListStart
        \resumeItem{Grew platform to \$1,000 monthly recurring revenue (MRR) within 3 months by acquiring paying therapist clients.}
        \resumeItem{Built and launched core features (billing, treatment planning, clinical notes) with Python, FastAPI, React, and Stripe, reducing documentation time for therapists by 40\%. Built and deployed with Docker on Railway through Git.}
        \resumeItem{Implemented secure HIPAA-compliant AWS infra (EC2, S3, RDS) with encryption, IAM, and VPC isolation.}
        \resumeItem{Selected for Telora Fellowship and engaged with Mokhtarzada Hatchery, refining strategy and pitching to investors.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer, University Career Center (UCC)}{Remote, New Jersey}
      {Full-Stack Software Engineering (Academic-Year Internship)}{}
      \resumeItemListStart
        \resumeItem{Built and maintained Intern for a Day (\href{https://ifad.umd.edu}{ifad.umd.edu}) serving 1,000+ students/cycle on FastAPI, React/TS, PostgreSQL.}
        \resumeItem{Built custom student matching algorithm integrating Google Gemini for semantic checks, halving coordinator time.}
        \resumeItem{Led a \$35K Do Good-funded upgrade adding RBAC, FERPA-aware PII controls, audit logs, and data-retention policies.}
        \resumeItem{Shipped CI/CD (GitHub Actions + Docker) and monitoring; query tuning and caching cut p50 page load $\sim$30\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Startup Software Engineer Intern, SPARK}{Remote, New Jersey}
      {Full Stack Software Development Internship}{}
      \resumeItemListStart
        \resumeItem{Built and deployed scalable web applications using React, Python, and FastAPI, improving UX load time by 35\%.}
        \resumeItem{Integrated Stripe, AWS Lambda, and ElevenLabs voice API for secure payments, cutting latency by 20\%.}
        \resumeItem{Designed backend microservices and REST APIs using PostgreSQL and Docker to support concurrent user sessions.}
      \resumeItemListEnd

    \resumeSubheading
      {SAR Synthetic Dataset Research Intern, Professor Triet Le}{College Park, Maryland}
      {Software/ML Research Assistant}{}
      \resumeItemListStart
        \resumeItem{Developed SAR dataset in MATLAB/Python/C to reduce data scarcity and enable self-supervised learning.}
        \resumeItem{Implemented a preprocessing pipeline (calibration, speckle filtering, normalization, tiling, augmentation) to improve model signal-to-noise and training stability.}
        \resumeItem{Benchmarked CNN baselines against classical ML (SVM/Random Forest) with k-fold CV on SAR classification, segmentation, and backscatter-regression tasks.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Audit.AI (Bitcamp 2024 Hackathon Winner)}{College Park, Maryland}
      {Full Stack Developer}{}
      \resumeItemListStart
        \resumeItem{Built a YOLOv6-based multimodal ML system using Python and PyTorch to detect misinformation at scale.}
        \resumeItem{Engineered scalable backend with MongoDB and Redis caching for real-time media auditing, earning best overall hack.}
      \resumeItemListEnd

    \resumeSubheading
      {askTestudo}{Georgetown, Maryland}
      {Lead Backend Developer}{}
      \resumeItemListStart
        \resumeItem{Trained an LLM chatbot with Azure OpenAI \& Retrieval-Augmented Generation (RAG) for precise query handling.}
        \resumeItem{Integrated vector search indexing, multimodal video responses, and chat UI in a React/FastAPI/MongoDB app.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, Java, JavaScript, TypeScript, C++, C, SQL, R, HTML, CSS \\
     \textbf{Frameworks \& Libraries:} React.js, Node.js, FastAPI, Flask, React Native, PyTorch, TensorFlow, Bootstrap \\
     \textbf{Cloud \& DevOps:} AWS, Azure, Google Cloud, Docker, Kubernetes, Cloudflare, GitHub Actions, CI/CD, Linux, Ubuntu \\
     \textbf{Databases \& Tools:} PostgreSQL, MongoDB, Redis, MySQL, Jupyter, Colab, VS Code, IntelliJ, Git, Eclipse, Bash
    }}
 \end{itemize}

\end{document}
